Merging merges, more or less

### 2015-03-04 2015mergingmerges/section/02-Machines.tex
ok

\subsection{Conversion of combinators}
The combinators from section~\ref{s:Combinators} can be converted to these DFAs quite easily.

Well, do it.
I'm still not sure, maybe just showing the pictures would be better.

>>>>

\subsection{Combinators}
Many interesting combinators can be described using these machines.
Below, the machines for some important combinators are given.
The machines are described in an almost BASIC-like syntax with numbered state labels before the colon, followed by the state, and then the transitions.
If the transitions are not shown, a @Unit@ transition to the next numbered state is implicit.
The combinator's output channel is assumed to be named @o@.

While writing combinators in this form is neither pleasant nor pretty, it only needs to be done once.
The implementation contains more combinators such as group by, append and indices of segment lengths.

\subsubsection{map f xs}
\begin{code}
10: Pull xs         (Some x => 20; None  => 90)
20: Out o (f x)
30: Release x       (Unit   => 10)

90: OutDone o
99: Done
\end{code}

\subsubsection{filter p xs}
\begin{code}
10: Pull xs         (Some x => 20; None  => 90)
20: If (p x)        (True   => 30; False => 40)
30: Out o x
40: Release x       (Unit   => 10)

90: OutDone o
99: Done
\end{code}

\subsubsection{zip xs ys}
\begin{code}
10: Pull xs         (Some x => 20; None  => 90)
20: Pull ys         (Some x => 30; None  => 80)
30: Out o (x, y)
40: Release x
50: Release y       (Unit   => 10)

80: Release x
90: OutDone o
99: Done
\end{code}

\subsubsection{merge xs ys}
\begin{code}
10: Pull xs         (Some x => 20; None  => 100)
20: Pull ys         (Some y => 30; None  => 201)
30: If (x <= y)     (True   => 40; False => 50)

40: Out o x
41: Release x
42: Pull x          (Some x => 30; None  => 101)

50: Out o y
51: Release y
52: Pull y          (Some y => 30; None  => 201)

-- xs is empty
100: Pull ys        (Some y => 101; None => 900)
101: Out o y
102: Release y      (Unit   => 100)

-- ys is empty
200: Pull xs        (Some x => 201; None => 900)
201: Out o x
202: Release x      (Unit   => 200)

900: OutDone o
901: Done
\end{code}

Figures 1-3 show automata for combinators @map@, @filter@ and @zip@.
To reduce clutter, these figures omit labels for @Unit@ transitions.

\input{figures/Combinators.tex}

\subsection{Code extraction}

Extracting imperative code from these machines is quite straightforward.
Variables are created for each 
Each state is converted to a basic block and given a unique identifier as its label.
